% This is "Conclusions.tex"
% A content sub-file of "TrustfullActionSugestion-Paper.tex"
\section{Conclusions}
Throughout this paper we addressed the work done to develop a Cognitive Trust Model capable of suggesting actions to improve Trust in a virtual agent. We first went through our thoughts about the lack of research done in the area of trust in \ac{HRI}, especially regarding trust improvement, and what we propose to address that issue. Then we went on to establish some background in \ac{HRI} concepts specific to the domain. In the next chapter we delved into some of the Cognitive Trust Models that we found. While there were many more aside from those discussed in this thesis, we wanted to focus on the ones that most closely related with the one we developed. Following that we presented our Trust Model, describing its 3 main components: Memory, Perception and Action Suggestion, and how they interact to compose our model. Due to problems finding a suitable evaluation scenario for our model, we then describe our second contribution of this thesis, a novel Trust and Rapport evaluation scenario, Quick Numbers, that aims to evaluate how ability and willingness jointly affect trust, by imposing to the participant the choice to entrust the agent, with their own earned resources, to play a game, in which the participant has some idea of the agent's ability. Finally we showed how we used the scenario to perform User Studies on the Trust Model. Unfortunately, the results can be considered either inconclusive, or right against our effort to improve Trust, as there was no apparent change in Trust measurements in conditions with and without the Action Suggestion module. Nevertheless, we believe that our contributions were significant by providing an implementable base from which other research projects in the same area may start. 